Scikit-learn: machine learning without learning the machinery

### 2014-05-21 article.tex
Intro to big data

\paragraph{What about big data?}
%
Partial fit, random projections, HashingVectorizer

>>>>

\paragraph{What about big data?}
%
``Big data'' is the latest trend of data analytics: applying machine
learning to large datasets can extract information so far unexploited.
These large datasets present of course new technical challenges, in
particular to be computationally tractable. It is important to
distinguish the case of very large number of samples, or very large
number of features. For a very large number of features, on-the-fly data
reductions, that exploit latent redundancy in the features, come in
handy. In scikit-learn, one could for instance resort to
random projections, that exploit the Johnson-Lindenstrauss lemma to give
good approximations of Euclidean distance in the datasets. In the
situation of a very large number of samples, some estimator expose
\emph{on-line} algorithms: they can be fit incrementally, with successive
calls to their {\tt partial\_fit} method, and converge in a small number
of passes on the data. To alleviate one of the main practical challenges of
big data, data-transfer latency, optimal data-fetching code can be used
in parallel with the calls to {\tt partial\_fit}.

Partial fit, random projections, HashingVectorizer
